The Hosting Environment of the Advanced Resource Connector middleware

### 2008-09-26 doc/hed/ARCHED_article.tex
Converting list of attributes to bullets and adding full stop after each.

That MCC also fills following Message Attributes in the incoming Message while passing to the next MCC:
\begin{enumerate}

@@

\item HTTP:RANGESTART - Range request start offset

\item HTTP:RANGEEND - Range request end offset

\item HTTP:ENDPOINT - URL or path as specified in HTTP request header

\item HTTP:* - Here * stands for any name. All HTTP options from HTTP request header are converted into Message Attributes named HTTP:\{option name\}

\item ENDPOINT - same as HTTP:ENDPOINT

>>>>

That MCC also fills following Message Attributes in the incoming Message while passing to the next MCC:
\begin{itemize}

@@

\item HTTP:RANGESTART - Range request start offset.

\item HTTP:RANGEEND - Range request end offset.

\item HTTP:ENDPOINT - URL or path as specified in HTTP request header.

\item HTTP:* - Here * stands for any name. All HTTP options from HTTP request header are converted into Message Attributes named HTTP:\{option name\}.

\item ENDPOINT - same as HTTP:ENDPOINT.
